Street network analysis is widely used to relate urban form to land-use intensity and travel behaviour, yet ``closeness'' centrality is inconsistently described, with cited formulas diverging from those implemented in software packages. This matters for contemporary analysis, where centralities are increasingly computed in localised (distance-threshold) forms to reduce edge effects and enable multi-scalar comparisons. In localised analysis, reachable node counts vary by origin. Because \emph{Closeness} and \emph{Normalised Closeness} divide by total distance, variation in node count conflates two effects: whether a given denominator is larger due to more nodes being reachable, or whether reachable nodes are more distant on average. This undermines comparability across locations. We clarify this mechanism, demonstrate reliable alternatives (\emph{Improved} and \emph{Harmonic} Closeness), and provide an openly reproducible workflow.

We test implications in Madrid, Spain, using street-network, land-use, and travel-survey data. We compute multiple formulations, including \emph{Closeness}, \emph{Normalised Closeness}, \emph{Improved}, \emph{Harmonic}, and \emph{Gravity}, for metric and angular distances across multiple radii, and relate them to land-use accessibility and trip volumes using Spearman correlations with spatially robust (block-bootstrap) uncertainty estimates. \emph{Closeness} shows negative associations with land-use intensity, while \emph{Normalised Closeness} shows weak associations. In contrast, \emph{Improved}, \emph{Harmonic}, and \emph{Gravity} remain stable and consistently positively associated across scales, consistent with their adoption in commonly used software packages. We conclude with practical guidance: prioritise formulations that scale appropriately with varying sub-graph sizes, and clearly document the precise formulations and workflows to support reproducibility and comparability of methods.
