\section{Introduction}

Streets form connections between diverse activities and places. While their functional role is apparent, their emergent properties are less so. It can be observed that particular sidewalks are livelier than others, that certain land uses cluster at particular locations, or that walkable and vibrant streets can become public destinations in their own right \cite{Jacobs1961}. Yet, without recourse to the incremental and evolutionary development typical of historical towns and cities, it is not straightforward to anticipate these dynamics for planned street networks \cite{Alexander1967}. Even if the benefits of compact and walkable forms of urban development are widely reported, new developments continue to prioritise vehicular movement to more distant places at the expense of pedestrians and connectivity to local street networks \cite{transport_for_new_homes_what_2025}. This is where network analytic methods are particularly relevant: by enabling the comparison of emergent properties of street configurations, they make it feasible to explore how these relate to potential activity and use.

Network analysis has been widely utilised across numerous disciplines, from early centrality methods in the study of telecommunication networks \cite{Shimbel1953} to more recent advances in social network analysis \cite{Wasserman1994}. The utilisation of graph theories for spatial problems can be traced to 1736 when Euler proposed a graph-based solution to the Königsberg Seven Bridges problem \cite{euler_solutio_1741}. In the 1950s and 1960s, Froshaug compared hierarchies of street networks by mapping them as simplified graphs with street intersections as nodes \cite{froshaug_visuelle_1959}. Space Syntax theory, developed by Hillier and colleagues in the late 1970s and early 1980s, integrated network measures with a social theory of space to analyse cities \cite{Hillier1984}, prompting wider adoption of street network analysis in urban design and planning.

This matters because localised analysis is now standard practice. It mitigates edge effects, enables cross-city comparisons, and permits multi-scalar investigation of network properties \cite{Turner2007, van_nes_introduction_2021}. A divergence has since emerged between the closeness centrality formulas generally cited in the literature and those implemented in widely used software packages. For global analysis on fixed-size graphs, such discrepancies may pass unnoticed. Localised analysis, however, operates on subgraphs of varying size defined by distance thresholds at each origin, and here the consequences are substantial.

The shift from global to localised methods required adaptation of the underlying mathematics, but this transition is not well documented. Packages offering radius-limited closeness analysis span a range of ecosystems: specialised tools such as \texttt{depthmapX} \cite{Hillier2012}, \texttt{Place Syntax Tool} \cite{stahle_place_2023}, \texttt{cityseer} \cite{simons_cityseer_2023}, \texttt{sDNA} \cite{cooper_sdna_2020}, and the \texttt{Urban Network Analysis} toolbox \cite{Sevtsuk2012}; as well as general-purpose libraries such as \texttt{igraph} \cite{csardi_igraph_2006}, \texttt{tidygraph}/\texttt{sfnetworks} \cite{pedersen_tidygraph_2024, vanderbie_sfnetworks_2021}, and \texttt{NetworkX} \cite{hagberg_networkx_2008}, which support localised analysis through cutoff parameters or explicit subgraph construction. Yet the closeness formulation used---and its behaviour under varying subgraph sizes---is frequently left implicit, and papers continue to cite formulations that differ from those actually computed. A researcher implementing the cited formula to replicate a published study may therefore obtain different results, potentially with reversed sign or negligible magnitude.

The issue sits within a broader context of reproducibility challenges in street network analysis, including differences in network representation \cite{feng_accessibility_2022, Marshall2018}, algorithmic variations \cite{krenz_kimon_developments_2022}, and inadequate control for edge effects \cite{Gil2017}. The divergence between cited and implemented closeness formulations represents a specific, tractable instance of these challenges, one with clear mathematical explanation and practical resolution.

\paragraph{What this paper adds:} We document a divergence between the closeness formulation cited in the street network analysis literature (\emph{Normalised Closeness}) and the variants implemented in computational packages (\emph{Improved Closeness}). We explain theoretically why this distinction matters for localised analysis: \emph{Closeness} exhibits sign reversal when subgraph sizes vary; \emph{Normalised Closeness} yields negligible associations; \emph{Improved} and \emph{Harmonic Closeness} yield values that increase with both node count and proximity. We demonstrate these behaviours empirically and provide an openly reproducible workflow.

\paragraph{Research questions:} \textbf{RQ1:} Do different closeness formulations behave differently under localised street network analysis? \textbf{RQ2:} Are these mathematical differences empirically detectable when centrality measures are correlated with urban indicators? We hypothesise that \emph{Closeness} will exhibit sign reversal under localised analysis because it conflates subgraph size with average distance, and that \emph{Normalised Closeness} will not correct this. By contrast, \emph{Improved} and \emph{Harmonic Closeness} should yield values that increase with both the number and proximity of reachable nodes. Section~\ref{closeness_centrality} develops this hypothesis formally; Sections~\ref{empirical-methodology}--\ref{data-analysis} demonstrate these differences empirically.
