\section{Discussion and Conclusions}\label{discussion}

The empirical results for Madrid are consistent with the theoretical hypothesis. Regarding \textbf{RQ1}, we find a meaningful distinction: mathematically defined \emph{Closeness} exhibits sign reversal when applied to localised street network analysis, correlating negatively with urban intensity where positive associations are expected. \emph{Normalised Closeness} does not correct this---it yields negligible associations. By contrast, \emph{Improved Closeness} and \emph{Harmonic Closeness} yield values that increase with subgraph size and proximity. Regarding \textbf{RQ2}, these behavioural differences manifest empirically: results hold for land-use accessibility and origin-destination trip counts, for length-weighted and unweighted variants, and for both metric and geometric distances.

The NAIN formulation ($N^{1.2}$), introduced in \cite{Hillier2012}, represents an intermediate case. It performs better than \emph{Normalised Closeness} but does not fully recover the behaviour of \emph{Improved Closeness}. NAIN was derived empirically with the aim of aligning values across different distance radii, not to address the underlying scaling issue with varying subgraph sizes.

Software developers have addressed this issue in practice, though implementations vary. \texttt{depthmapX} \cite{turner_depthmapx_2020}, \texttt{Place Syntax Tool} \cite{stahle_place_2023}, and \texttt{cityseer} \cite{simons_cityseer_2023} implement or offer a form of \emph{Improved Closeness}, and in some cases also \emph{Harmonic Closeness} or the \emph{Gravity Index}. Generic libraries such as \texttt{NetworkX} \cite{hagberg_networkx_2008} and \texttt{igraph} \cite{csardi_igraph_2006} also provide these formulations. Other specialised packages take different approaches: \texttt{sDNA} \cite{cooper_sdna_2020} outputs a gravity-like measure (NQPD), while the \texttt{Urban Network Analysis} toolbox \cite{Sevtsuk2012} provides a \emph{Gravity Index}.

The reproducibility problem affects researchers who implement closeness centrality from cited formulas without access to original code, or who review or teach network centrality methods based on commonly cited formulations. We suspect that one reason this misattribution persists is that even though \emph{Normalised Closeness} is typically cited, many studies rely on packages that implement forms of closeness that work for localised analysis. In such cases, outputs perform as expected even if users are under mistaken impressions about the formulation, while replication without code can yield different results, potentially with reversed sign or negligible magnitude.

These ambiguities warrant further investigation into the robustness of currently held assumptions regarding the relative performance of different centralities and forms of distance heuristic. Earlier studies that cite \emph{Normalised Closeness} without providing open code, that select small geographic areas, or that do not buffer boundaries to control edge effects \cite{Turner2007, Porta2006} may warrant re-examination---not because their results are necessarily wrong, but because the relationship between cited methods and computed results is unclear. We acknowledge that some studies using \emph{Normalised Closeness} may have operated under conditions where the distinction matters less---for example, global analysis on fixed graphs, or localised analysis at thresholds where subgraph sizes vary minimally.

We consequently encourage the use of openly available reference datasets and reproducible workflows, as we have made available in this study, so that different measures can be benchmarked openly and collaboratively against common points of reference. This would facilitate the evaluation of newly available methods against established variants while accounting for differences which might otherwise be attributable to variations in urban context or data representation. It would also help uncover situations such as the widespread misconceptions on closeness centralities discussed in this study.

This study uses a single city (Madrid); correlation magnitudes will differ across urban contexts depending on street network morphology, density gradients, and land-use distributions. However, our contribution concerns the existence and direction of formulation differences, not their precise magnitude. The theoretical mechanism is mathematical: \emph{Closeness} conflates subgraph size with average distance; \emph{Normalised Closeness} neutralises meaningful variation; \emph{Improved Closeness} and \emph{Harmonic Closeness} avoid this conflation through different mechanisms---the former by dividing by average distance, the latter by summing distance reciprocals. This mechanism applies to any network where subgraph sizes vary by origin, which is why developers of domain-specific packages adopted these formulations.

This has implications for interpreting existing literature: studies using \texttt{Depthmap} or similar tools likely produced valid results regardless of cited formulations; studies using generic network packages or custom implementations warrant scrutiny regarding which formula was actually computed; and comparative evaluations of closeness formulations should verify that implementations match cited formulas.

Earlier studies that cite \emph{Normalised Closeness} without providing open code, that select small geographic areas, or that do not buffer boundaries to control edge effects \cite{Turner2007, Porta2006} may warrant re-examination---not because their results are necessarily wrong, but because the relationship between cited methods and computed results is unclear.

\subsection{Practical Guidance}

For localised street network analysis, we recommend:
\begin{enumerate}
  \item Use closeness formulations that scale with varying subgraph sizes: \emph{Improved Closeness}, \emph{Harmonic Closeness}, or \emph{Gravity}-based measures;
  \item Document the precise formulation used, not just the generic term `closeness';
  \item Provide code or specify the software package and version to enable replication;
  \item When using generic network packages, verify that the closeness implementation is appropriate for localised analysis.
\end{enumerate}

\subsection{Limitations}

This study uses a single city (Madrid), which is appropriate because our argument is mathematical: the theoretical reasons why formulations diverge under localised analysis apply to any network where subgraph sizes vary by origin. The Madrid case demonstrates that this divergence has empirically detectable consequences. Correlation magnitudes will differ across urban contexts (e.g., cities with linear high streets, polycentric structures, or car-oriented development), but our contribution concerns the existence and direction of formulation differences, not their precise magnitude. The empirical analysis is diagnostic and cross-sectional: correlations reveal that formulations behave differently, not that any particular formulation correctly captures urban accessibility. We do not model causal relationships between centrality and land-use.

\subsection{Conclusion}

The divergence between cited closeness formulations and software implementations creates a reproducibility barrier in street network analysis. Mathematical \emph{Closeness} exhibits sign reversal under localised analysis; \emph{Normalised Closeness} yields negligible associations; \emph{Improved} and \emph{Harmonic Closeness} yield values that increase with subgraph size and proximity. Researchers should use appropriate formulations for localised analysis and document computational methods precisely. We provide open code and data to support reproducibility and to serve as a reference for future methodological comparisons.
