%==============================================================
% ISPRS International Journal of Geo-Information (IJGI) — MDPI submission
%
% Uses Definitions/mdpi.cls. All shared content (sections, tables,
% generated numbers, supplementary, images, plots, references.bib) is
% resolved from the parent paper/ directory via TEXINPUTS by build.py —
% no copies, no symlinks. Mirrors the paper/epb_submission/ approach.
%
% Journal is a single class option below: change "ijgi" to e.g.
% "urbansci" to retarget; the bibliography style (mdpi.bst) is unchanged.
%==============================================================
\documentclass[ijgi,article,submit,moreauthors]{Definitions/mdpi}

%-------------------------------------------------------------
% MDPI internal front-matter placeholders (filled by the Editorial Office)
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2026}
\copyrightyear{2026}
\datereceived{ }
\daterevised{ }
\dateaccepted{ }
\datepublished{ }

%-------------------------------------------------------------
% Extra packages NOT already loaded by mdpi.cls.
% (mdpi.cls already provides amsmath, amssymb, booktabs, array, caption,
%  natbib, hyperref, url, geometry, graphicx, xcolor, microtype, ...)
% The shared content only needs siunitx (for the \n/\nc/\pct macros); the
% sections use plain tabular, so longtable/rotating/mdframed/moreverb are
% omitted (moreverb's \listing and mdframed's \begin{document} patching
% both clash with mdpi.cls).
\usepackage{siunitx}
% catchfile pre-reads the shared abstract into static tokens. MDPI's
% \abstract is a command (not an environment like SAGE's), and a live
% \input inside its argument corrupts the class's argument re-scan at
% \begin{document} (TeX-capacity recursion). catchfile avoids that.
\usepackage{catchfile}

% No-op \todo so the shared section files compile without todonotes.
\providecommand{\todo}[2][]{}

\captionsetup[table]{skip=14pt}

\sisetup{
  detect-all,
  group-separator = {,},
  group-minimum-digits = 5
}

% Shared numeric-formatting macros (identical to the working build).
\newcommand{\n}[1]{\num{#1}}
\newcommand{\nc}[1]{\num[group-minimum-digits=4]{#1}}
\newcommand{\pct}[1]{\n{#1}\%}
\newcommand{\distm}[1]{\n{#1}m}
\newcommand{\distkm}[1]{\n{#1}km}

% Generated from upstream analysis outputs; do not edit by hand.
\input{generated/paper_numbers}

% Resolve cross-references to the separate supplementary document (Figure S#,
% Table S#) so the split manuscript still prints the correct numbers. The
% supplementary file (supplementary.tex) reciprocally references main-text
% equations via xr. build.py compiles both in interleaved passes so the .aux
% files are mutually available.
\usepackage{xr}
\externaldocument{supplementary}

%-------------------------------------------------------------
% Front matter (single-blind: IJGI reviewers see the authors)
\Title{Divergence in Closeness Centrality Formulations: Implications for Reproducibility in Street Network Analysis}

% ORCID iDs (verified against the ORCID registry). Each \orcidauthorX feeds the
% \orcidX{} icon-link appended after the matching name in \Author below; ORCID is
% also entered separately in the SuSy submission form.
\newcommand{\orcidauthorA}{0000-0003-3790-0638} % Gareth Simons
\newcommand{\orcidauthorB}{0000-0001-6077-7282} % Kimon Krenz
\newcommand{\orcidauthorC}{0009-0003-8520-3551} % Sepehr Zhand

\Author{Gareth Simons $^{1,}$*\orcidA{}, Kimon Krenz $^{1}$\orcidB{} and Sepehr Zhand $^{1}$\orcidC{}}

\AuthorNames{Gareth Simons, Kimon Krenz and Sepehr Zhand}

\address{%
$^{1}$ \quad Space Syntax Laboratory, The Bartlett School of Architecture, University College London, London, UK; gareth.simons@ucl.ac.uk (G.S.); k.krenz@ucl.ac.uk (K.K.); sepehr.zhand.18@ucl.ac.uk (S.Z.)}

\corres{Correspondence: gareth.simons@ucl.ac.uk}

% Shared abstract, read as static tokens (see catchfile note above).
\CatchFileDef{\sharedabstract}{sections/0_abstract.tex}{}
\abstract{\sharedabstract}

\keyword{closeness centrality; network centrality; integration; street networks; urban analytics; reproducibility; space syntax; accessibility}

%==============================================================
\begin{document}

% Auto-generated statistics macros from the analysis scripts.
\input{tables/summary_stats_segments.tex}
\input{tables/summary_stats_survey.tex}

%-------------------------------------------------------------
\input{sections/1_networks}
\input{sections/3_centralities}
\input{sections/4_methods}
\input{sections/6_analysis}
\input{sections/7_conclusion}

%-------------------------------------------------------------
% Back matter
% Supplementary materials are a SEPARATE file (supplementary.tex -> supplementary.pdf),
% per the MDPI submission system (do not bundle into the manuscript package).
\supplementary{The following supporting information is submitted as a separate file. Section S1 (Additional Centralities): the Gravity Index, Betweenness, NACH, and length-weighting formulations, with Figure S1 (spatial impedance decay), and Figure S2 and Table S1 (length-weighted closeness formulations). Section S2 (Additional Figures and Tables): Figure S3 (PCA loadings); Figure S4 (angular closeness comparison); Figures S5--S8 (angular and length-weighted centrality--land-use and trip-survey correlation grids); and Tables S2--S6 (descriptive statistics, Moran's $I$, effective sample size, and block-bootstrap confidence intervals).}

\authorcontributions{Conceptualization, methodology, software, formal analysis, data curation, writing---original draft preparation, and visualization, G.S.; writing---review and editing, K.K. and S.Z. All authors have read and agreed to the published version of the manuscript.}

\funding{This research received funding from the European Union's Horizon Europe Research and Innovation Programme under Grant Agreement No.\ 101078890; from UK Research and Innovation (UKRI) under the UK government's Horizon Europe funding guarantee under grant numbers 10052856 and 10050784 (G.S.\ and S.Z.); and from the UKRI PHI-UK Healthy Urban Places project under grant number MR/Y022785/1 (K.K.).}

\institutionalreview{Not applicable. This study used publicly available spatial datasets and did not involve humans or animals.}

\informedconsent{Not applicable.}

\dataavailability{The data-preparation workflow is openly available at \url{https://github.com/songololo/ua-dataset-madrid} (version tagged v3.0.0). The analysis code and plot-generation pipeline are openly available at \url{https://github.com/songololo/paper-centrality} (version tagged v0.8.3).}

\acknowledgments{The initial analysis and the first manuscript drafts were completed without the use of generative AI. Generative AI (Claude, Anthropic) was used only in subsequent stages: to assist with editorial revisions and word-count reductions, and in the later stages of analysis to help prepare the plots, figures, and tables. The authors reviewed and edited all output and take full responsibility for the content of this article.}

\conflictsofinterest{The authors declare no conflicts of interest.}

%-------------------------------------------------------------
\reftitle{References}
\externalbibliography{yes}
% Bibliography style is set by mdpi.cls (Definitions/mdpi.bst); do not re-declare.
\bibliography{references}

\end{document}
